---
title: ""
output: html_document
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 20)
```

```{r, include = F}
############### Season elevation plots by species detections
#######   tabbed by species
# read data
library(tidyverse)
library (knitr)

# plot.data <- readRDS('./_data/carnivoreDetectionsBySiteElev_plot.RDS')
# # str(plot.data)
# 
# 
# species <- names(plot.data)
# species<-species[species != ""]

in.path<-'./speciesDetectionPlots_images'
plots<-list.files(in.path)
plot.names<-gsub('.png', '', plots)
plots<-file.path(in.path,plots)

plot.list<-list()

for(i in 1:length(plot.names)){
 # plot.list[[plot.names[i]]]<-file.path(in.path,plots[i])
  plot.list[[plot.names[i]]]<-file.path(plots[i])
}


```
<br><br><br><br><br>


#### Species detections by elevation across survey years


##  {.tabset}

### `r tab.plot<-names(plot.list[1]); tab.plot`

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```

### `r tab.plot<-names(plot.list[2]); tab.plot`

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[3]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```

`r tab.plot<-names(plot.list[4]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[5]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[6]); tab.plot`

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[7]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[8]); tab.plot`

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[9]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


### `r tab.plot<-names(plot.list[10]); tab.plot`

```{r  echo=FALSE, out.width = '100%'}
knitr::include_graphics(plot.list[[tab.plot]])
```


# {-}