---
title: ""
output: html_document
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 22)
```

```{r, include = F}
############### Season elevation plots by species detections
#######   tabbed by species
# read data
library(tidyverse)
library (knitr)

# plot.data <- readRDS('./_data/carnivoreDetectionsBySiteElev_plot.RDS')
# # str(plot.data)
# 
# 
# species <- names(plot.data)
# species<-species[species != ""]

in.path<-'./speciesDetectionMaps_images'
plots<-list.files(in.path)
plot.names<-gsub('.png', '', plots)

plots<-file.path(in.path,plots)

plot.names.tab<-tibble(data.frame(matrix(unlist(strsplit(plot.names, '_')), nrow = length(plot.names), byrow = T),stringsAsFactors = F))
names(plot.names.tab)<-c('sa','sp')
plot.names.tab$path<-plots

# unique(plot.names.tab$sa)
species <- unique(plot.names.tab$sp)


```
<br><br><br><br><br>


### Species detections by survey year

<br><br/>
<br><br/>





```{r, include = F}
##########################################################################################
#########################################  2016
plots.pr<-plot.names.tab %>% 
  filter(sa == "mammothLakesBasin" | sa == "northforkBishopCreek" | sa == "rockCreek")
width<-'50%'
```


#### 2016, clockwise from top left
#### Mammoth Lakes Basin, Rock Cr., North Fork Bishop Cr.





##  {.tabset}

### `r pl.sp<-species[1]; pl.sp`

```{r  image_grobs, fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[2]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[3]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[4]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[5]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[6]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[7]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[8]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[9]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

### `r pl.sp<-species[10]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sa == "mammothLakesBasin" & sp == pl.sp) %>% select(path) %>% c()
plot2<-plots.pr %>% filter(sa == "rockCreek" & sp == pl.sp) %>% select(path) %>% c()
plot3<-plots.pr %>% filter(sa == "northforkBishopCreek" & sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
knitr::include_graphics(plot2[[1]])
knitr::include_graphics(plot3[[1]])
```

##




<br><br><br><br>





```{r, include = F}
####################################################################################################################
#############################  2017

plots.pr<-plot.names.tab %>% 
  filter(sa == "humphreysBasin")
width<-'90%'
```

#### 2017, Humphreys Basin





##  {.tabset}

### `r pl.sp<-species[1]; pl.sp`

```{r   fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[2]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[3]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[4]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[5]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[6]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[7]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[8]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[9]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[10]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

##




<br><br><br><br>




```{r, include = F}
####################################################################################################################
#############################  2018

plots.pr<-plot.names.tab %>% 
  filter(sa == "monoCreek")
width<-'90%'
```

#### 2018, Mono Creek





##  {.tabset}

### `r pl.sp<-species[1]; pl.sp`

```{r   fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[2]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[3]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[4]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[5]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[6]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[7]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[8]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[9]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[10]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

##


<div/>

<br><br><br><br>




```{r, include = F}
####################################################################################################################
#############################  2019

plots.pr<-plot.names.tab %>% 
  filter(sa == "ritterRange")
width<-'90%'
```

#### 2019, Ritter Range





##  {.tabset}

### `r pl.sp<-species[1]; pl.sp`

```{r   fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[2]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[3]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[4]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[5]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[6]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[7]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[8]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[9]; pl.sp`

```{r  fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

### `r pl.sp<-species[10]; pl.sp`

```{r fig.show = 'hold', echo=FALSE, out.width = width, fig.align='default'}
plot1<-plots.pr %>% filter(sp == pl.sp) %>% select(path) %>% c()

knitr::include_graphics(plot1[[1]])
```

##





